---
title: "Hello World!"
format: gfm
editor: visual
---

# Introduction

This project investigates the 2025 New York City Restaurant Inspection Results data from NYC OpenData. I love trying new restaurants in the city and am adamant that the places we go to pass their health grades! As a first step, I would like to understand the breakdown of grades for restaurants in my neighborhood (as defined by being in the same area code) and identify the restaurants to avoid.

\*Source file: <https://data.cityofnewyork.us/Health/DOHMH-New-York-City-Restaurant-Inspection-Results/43nn-pn8j/about_data>

```{r}
nyc_restaurant_grades <- read.csv("https://raw.githubusercontent.com/JessChen0/my-first-project/refs/heads/main/DOHMH_New_York_City_Restaurant_Inspection_Results_2025.csv")
```

## Analysis

### Restaurant Grades in 10029 area code (in 2025)

```{r}
library(dplyr)
library(janitor)
library(tidyverse)
library(knitr)

nyc_restaurant_grades_cleaned <- nyc_restaurant_grades %>% filter(ZIPCODE=="10029")
nyc_restaurant_grades_cleaned <- nyc_restaurant_grades_cleaned %>% clean_names() 
nyc_restaurant_grades_cleaned <- nyc_restaurant_grades_cleaned[c("dba","boro","cuisine_description","grade","council_district")]
nyc_restaurant_grades_cleaned <- unique(nyc_restaurant_grades_cleaned)
nyc_restaurant_grades_cleaned %>% count(grade)
```

### Restaurant Grades in 10029 area code (in 2025) graph

```{r}
ggplot(nyc_restaurant_grades_cleaned, aes(x=grade)) + geom_bar(fill="blue") + ggtitle(paste0("Restaurant Grades in zip code 10029 (2025)"))
```
Where N = not graded yet, P and Z = pending.

### List of C grade restaurants to avoid!

```{r}
nyc_restaurants_c_only <- nyc_restaurant_grades_cleaned %>% filter(grade=="C"|grade=="B")
nyc_restaurants_c_only %>% select(dba,cuisine_description,grade)
```

## Conclusions

In this project, I have confirmed that majority of restaurants in my neighbourhood have A grades.  Furthermore, I have identified the 20 grade B and C restaurants that I plan to avoid due to their violations.  

If time allows, further analysis of violation types, grade distributions compared with other neighborhoods and boroughs would be interesting.